\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-06-12 implementation.tex
.

We benchmarked our implementation and compared it with S3CAM.  The
preliminary results are tabulated in~\tabref{res-rel}. We used few of
the benchmarks described in \cite{zutshi2014multiple}, including the
Van der Pol oscillator, Brusselator, Lorenz attractor and the
Navigation benchmark. We also tried PWA-Rel on the insulin
benchmark~\cite{chenformal} and lane change maneuver
benchmark~\cite{althoff2012reachability}. PWA-Rel was compared with
S3CAM by running both $10$ times with different seeds (as both use
randomized algorithms), and their running times were averaged. PWA-Rel
was evluated with both the symbolic BMC SAL (PWA-Rel+SAL) and the
explicit BMC (PWA-Rel+OPT).  \todo{SatEx was also tried, but ...}. We
tabulate both the total time taken by PWA-Rel+SAL and PWA-Rel+OPT to
compute the counter-example and compare against an implementation of
S3CAM.  Different abstraction parameters are used for S3CAM and
PWA-Rel, due to the differences in which they operate. PWA-Rel
requires a finer abstraction to begin with in order to minimize the
modeling errors. On the other hand, a coarser abstraction as the
initial abstraction works better for S3CAM due to the expensive
refinement procedure involved.~\footnote{In all our experiments we
used $1$-relational modeling to create the transition system from $G$.
This was determined to be a good trade-off between longer simulations
and increase in precision, with respect to the mentioned benchmarks.}

>>>>

We benchmarked our implementation and compared it with S3CAM.  The
preliminary results are tabulated in~\tabref{res-rel}. We used few of
the benchmarks described in \cite{zutshi2014multiple}, including the
Van der Pol oscillator, Brusselator, Lorenz attractor and the
Navigation benchmark. We also tried PWA-Rel on the insulin
benchmark~\cite{chenformal} and lane change maneuver
benchmark~\cite{althoff2012reachability}. PWA-Rel was compared with
S3CAM by running both $10$ times with different seeds (as both use
randomized algorithms), and their running times were averaged. PWA-Rel
was evluated with both the symbolic BMC SAL (PWA-Rel+SAL) and the
explicit BMC (PWA-Rel+OPT). %\todo{SatEx was also tried, but ...}.
We
tabulate both the total time taken by PWA-Rel+SAL and PWA-Rel+OPT to
compute the counter-example and compare against an implementation of
S3CAM.  Different abstraction parameters are used for S3CAM and
PWA-Rel, due to the differences in which they operate. PWA-Rel
requires a finer abstraction to begin with in order to minimize the
modeling errors. On the other hand, a coarser abstraction as the
initial abstraction works better for S3CAM due to the expensive
refinement procedure involved.~\footnote{In all our experiments we
used $1$-relational modeling to create the transition system.
This was determined to be a good trade-off between longer simulations
and increase in precision, with respect to the mentioned benchmarks.}
